Effectiveness of Indirect Interventions for Reducing Mortgage Defaults

### 2022-04-28 outputs/paper/paper.Rmd
update title

---
title: "Indirect Interventions for Stabilizing Housing Markets"
subtitle: "Reproduction of Unemployment Insurance as a Housing Market Stabilizer (Hsu, Matsa, and Melzer 2018)"
author: 
  - Roy Chan
thanks: "Code and data are available at: https://github.com/chan-roy/HousingMarkets"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Preventing home foreclosures due to their associated costs is a key concern for policymakers during periods of economic instability. (Hsu, Matsa, and Melzer 2018) investigate the impact of unemployment insurance (UI) to stabilize the housing market in the United States, evaluating that UI expansions during the Great Recession aided in preventing foreclosures and stabilized home values. This paper replicates the analysis of their study and investigates alternative factors that impacted foreclosure rates. \\textbf{Keywords:} housing market stability, personal finance, great recession, unemployment insurance, foreclosures, economic policy, united states"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "Effectiveness of Indirect Interventions for Reducing Mortgage Defaults"
subtitle: "Reproduction of Unemployment Insurance as a Housing Market Stabilizer (Hsu, Matsa, and Melzer 2018)"
author: 
  - Roy Chan
thanks: "Code and data are available at: https://github.com/chan-roy/HousingMarkets"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Preventing home foreclosures due to their associated costs is a key concern for policymakers during periods of economic instability. (Hsu, Matsa, and Melzer 2018) investigate the impact of unemployment insurance (UI) to stabilize the housing market in the United States, evaluating that UI expansions during the Great Recession aided in preventing foreclosures and stabilized home values. This paper replicates the analysis of their study and investigates alternative factors that impacted foreclosure rates. \\textbf{Keywords:} housing market stability, personal finance, great recession, unemployment insurance, foreclosures, economic policy, united states"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
